Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-19 paper.qmd
Updated the Figure 15 title
Updated Figure 15 letters in 2D layouts

nldr_mnist3 <- phate_mnist |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("c") +
  theme(aspect.ratio = 1)

@@

nldr_mnist4 <- trimap_mnist |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("d") +
  theme(aspect.ratio = 1)

@@

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the MNIST digit 1 data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). Layout c is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-mnist-mse
#| fig-pos: H
#| out-height: 100%

>>>>

nldr_mnist3 <- phate_mnist |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("c", position = c(0.94, 0.92)) +
  theme(aspect.ratio = 1)

@@

nldr_mnist4 <- trimap_mnist |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("d", position = c(0.86, 0.92)) +
  theme(aspect.ratio = 1)

@@

```{r}
#| fig-cap: "Assessing which of the 5 NLDR layouts on the MNIST digit 1 data is the better representation using MSE for varying binwidth ($a_1$). Colour used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-e). All the layouts appear to be very similar. Layout c is universally poor. Layouts a that show two close clusters are universally suboptimal. Layout a is the best choice."
#| label: fig-mnist-mse
#| fig-pos: H
#| out-height: 100%
